Arc Blanc: a real time ocean simulation framework

### 2025-01-28 paper.tex
Clarify c choice
Fixed typo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stability}
\label{subsec:stability}
The stability of the scheme defined by Equation (\ref{eq:fdm_scheme_corrected}) is related to the CFL condition (for Courant–Friedrichs–Lewy), here given as follows:
\begin{equation}
	\frac{c^2dt^2}{\delta^2}\leq 0.5
\end{equation}
The parameter $dt$ is considered fixed throughout the simulation.
One contribution of this article is to adapt the simulation's parameters $c$ and $\delta$ to the CFL, as presented below.

Preliminary tests have shown that $\delta$ must be small for a low velocity $\mathbf{v_M}(t)$ of $M$.
Moreover, $\delta$ must be large enough for $Z$ to encompass $M$ and the waves generated by $M$.
The size of $M$ is defined from its bounding box $(b_x, b_y, b_z)$ as $S(M)=\max(b_x, b_z)$.
\Framework lets the user define the bounds $\delta_{min}$ and $\delta_{max}$ so that $Z$ is at least twice as large as $M$.
Then $\delta$ is defined as follows:
\begin{equation}
	\delta =
	\begin{cases}
		0.999~dt                    & ~~ \text{if}~||\mathbf{v_M}(t)||<1    \\
		||\mathbf{v_M}(t)||0.999~dt & ~~ \text{if}~||\mathbf{v_M}(t)||\geq1
	\end{cases}
\end{equation}
Finally $\delta$ is clamped between $\delta_{min}$ and $\delta_{max}$.
The value of $c$ is deduced from $\delta$ and $dt$ to validate the CFL as follows:
\begin{equation}
	c = \sqrt{0.49} \frac{\delta}{dt}
\end{equation}

@@

Hence, for a body $M$ the wave generation relies on two different steps:
First, a mask is defined from this list of 3D points, corresponding to the vertices of $Z$ contained into one intersected polygons.
Second, the height $h$ of each point in the mask is determined using an ad hoc function.
These two steps are detailed in the following two sections.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stability}
\label{subsec:stability}
The stability of the scheme defined by Equation (\ref{eq:fdm_scheme_corrected}) is related to the CFL condition (for Courant–Friedrichs–Lewy), here given as follows:
\begin{equation}
\label{equa:cfl}
	\frac{c^2dt^2}{\delta^2}\leq 0.5
\end{equation}
The parameter $dt$ is considered fixed throughout the simulation.
One contribution of this article is to adapt the simulation's parameters $c$ and $\delta$ to the CFL, as presented below.

Preliminary tests have shown that $\delta$ must be small for a low velocity $\mathbf{v_M}(t)$ of $M$.
Moreover, $\delta$ must be large enough for $Z$ to encompass $M$ and the waves generated by $M$.
The size of $M$ is defined from its bounding box $(b_x, b_y, b_z)$ as $S(M)=\max(b_x, b_z)$.
\Framework lets the user define the bounds $\delta_{min}$ and $\delta_{max}$ so that $Z$ is at least twice as large as $M$.
Then $\delta$ is defined as follows:
\begin{equation}
	\delta =
	\begin{cases}
		0.999~dt                    & ~~ \text{if}~||\mathbf{v_M}(t)||<1    \\
		||\mathbf{v_M}(t)||0.999~dt & ~~ \text{if}~||\mathbf{v_M}(t)||\geq1
	\end{cases}
\end{equation}
Finally $\delta$ is clamped between $\delta_{min}$ and $\delta_{max}$.
The value of $c$ is deduced from $\delta$ and $dt$ to ensure that the inequality in Equation \ref{equa:cfl} is always satisfied:
\begin{equation}
	c = \sqrt{0.49} \frac{\delta}{dt}.
\end{equation}
This choice of $c$ ensures numerical stability.

@@

Hence, for a body $M$ the wave generation relies on two different steps:
First, a mask is defined from this list of 3D points, corresponding to the vertices of $Z$ contained in one intersected polygons.
Second, the height $h$ of each point in the mask is determined using an ad hoc function.
These two steps are detailed in the following two sections.
